---
title       : Shiny App in  a Slidify Deck
author      : Ramnath Vaidyanathan
framework   : io2012
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, shiny]       # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
github      : {user: ramnathv, repo: shinySlidify}
---

## Introduction

This is a demo of how to add multiple Shiny apps to a Slidify deck. I hope to document this better, but for now the basic idea is to put the UI as a slide, wrapped in the utility function `sidebar`, and the server code as an R file named `app*.R` in the `apps` folder.

Slidify the deck and use `runApp` to run the Shiny application!

```{r}
library(shiny); library(knitr)
opts_chunk$set(echo = F, results = 'asis', comment = NA, cache = FALSE)
sidebar <- function(...){
  cat(as.character(div(class = 'row-fluid', ...)))
}
```

<style>body{background-color: black;}</style>

---

## Example 1: DistPlot

```{r}
sidebar(
   sidebarPanel(
      sliderInput("obs",  "", 0, 1000, 500)
   ),
   mainPanel(
      plotOutput("distPlot")
   )
)
```

<div class='alert alert-info'>
<p>For some reason, the plot doesn't load at first sometimes. Clicking `Inspect Element` seems to activate its rendering.</p>
</div>


---

## Example 2: Probability Distributions

```{r}
sidebar(
  sidebarPanel(
    selectInput("dist", "Distribution:", list(
      "Normal" = "norm", 
      "Exponential" = "exp", 
      "Uniform" = "unif",
      "Log-Normal" = "lnorm")
    ),
    numericInput('n', 'Number of Observations', value = 500, min = 1, max = 1000)
  ),
  mainPanel(
    plotOutput(outputId = "plot1", height = "300px")
  )
)
```

<div class='alert alert-info'>
<p>For some reason, the plot doesn't load at first sometimes. Clicking `Inspect Element` seems to activate its rendering.</p>
</div>


---

## Example 3: Interactive table

```{r}
sidebar(
  sidebarPanel(
    checkboxInput(inputId = "pageable", label = "Pageable"),
    conditionalPanel(
     "input.pageable==true",
     numericInput(inputId = "pagesize",
     label = "Countries per page",10)
    )
  ),
  mainPanel(
   htmlOutput("myTable")
  )
)
```

---

## Example 4: Animated Geo Chart


```{r}
sidebar(
  sidebarPanel(
    sliderInput("Year", "Election year to be displayed:", 
      min=1932, max=2012, value=2012,  step=4,
      format="###0",animate=TRUE)
  ),
  mainPanel(
    h3(textOutput("year")),
    htmlOutput("gvis")
  )
)
```

   
